---
title: "STAT390: Lab 1"
author: "Ken"
date: "2023-10-03"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
setwd("C:/Users/jetz1/school/stat390")
library("dplyr")
library("Hmisc")
```

```{r}
titanic <- read.csv("titanic.csv", header = TRUE)
View(titanic)
age <- titanic$age
summary(age)
describe(titanic)
count <- table(titanic$sex, titanic$pclass)
survived <- table(titanic$sex[titanic$survived == 1], titanic$pclass[titanic$survived == 1])
survived
```

header = T, tells R to ignore the first row in the CSV because those are the column names. The options for header is TRUE or FALSE.

The data set contains 8 variables: pclass, survived, sex, age, sibsp, parch, fare, embarked.

Age statistics:
Minimum: 0.1667
Maximum: 80
Mean: 29.81
1st Quartile: 21
3rd Quartile: 39

There were 282 people in 1st class, 261 in 2nd, and 500 in 3rd. 425 passengers survived. There were 386 female and 657 male passengers. 10% of the passengers were 50 years and older.

The breaks splits up the data into meaningful groups.